### 2019-06-18 2-Chapters/4-Chapter/IEEE_WCNC_2019__DemoICT.git/main.tex
Almost done for this Ch1 ?

\textbf{Related works.}
% \TODOL{Est-ce que je fais ça ici ou à la fin du chapitre 5 ? Ou peut-être en chapitre 1, ça ferait du contenu au chapitre 1...}
%
We evoke here some previous works that similarly implemented proof-of-concepts to show that reinforcement learning algorithms can be used within real-world wireless communications.
Starting from $2010$, the works of Wassim Jouini \cite{Jouini09,Jouini10,Jouini12} were the first ones to propose to use Reinforcement Learning for Cognitive Radio, especially MAB and the \UCB{} algorithm, and from $2014$, proof-of-concepts were developed by Christophe Moy and his student Clément Robert \cite{RobertSDR2014,MoyWSR2014}.
In $2015$ and $2016$, Christophe Moy continued to work on this direction, with a PhD student (Navikkumar Modi) and post-doc (Sumit J. Darak) in our team SCEE, for the following publications
\cite{darak2016bayesian,Darak16,modiDemo2016,kumar2016two}.
Since $2017$, Sumit J. Darak and his team at IIIT Delhi have been very active in the research on cognitive radio using multi-armed bandits, and some of their recent works are illustrated with real-world demo using USRP and the MATLAB/Simulink system
\cite{KumarYadav2018,SawantKumar2018,JoshiKumar2018}.

>>>>

\textbf{Related works.}
% \TODOL{Est-ce que je fais ça ici ou à la fin du chapitre 5 ? Ou peut-être en chapitre 1, ça ferait du contenu au chapitre 1...}
% FIXED j'en parle au chapitre 1
%
This work is new for the IoT context, but previous works have similarly implemented proof-of-concepts to show that Reinforcement Learning (RL) algorithms can be used within real-world wireless communications.
Starting from $2010$, the works of W. Jouini and C. Moy \cite{Jouini09,Jouini10,Jouini12} were among the first ones to propose to use RL for Cognitive Radio, especially MAB and the \UCB{} algorithm, and proof-of-concepts were developed with C. Robert from $2013$ \cite{RobertSDR2014,MoyWSR2014}.
Between $2015$ and $2017$, C. Moy, N. Modi and S. Darak (of our team SCEE) continued to work on this direction \cite{darak2016bayesian,Darak16,modiDemo2016,kumar2016two}.
Since $2017$, S. Darak and his team at IIIT Delhi (India) have been very active in the research on CR using MAB, and some of their recent works are illustrated with real-world demo using USRP and the MATLAB/Simulink system
\cite{KumarYadav2018,SawantKumar2018,JoshiKumar2018}.

### 2019-06-18 2-Chapters/5-Chapter/chapter5.tex
Almost done for this Ch1 ?

% ----------------------------------------------------------------------------
\subsection{Inspirations from Cognitive Radio Proof-of-Concepts}
\label{sub:5:USRPdemos}

Similarly to our demonstration of multi-armed bandit learning in an IoT network that we presented in the previous Chapter~\ref{chapter:4} in Section~\ref{sec:4:gnuradio},
we list here some related works, dating back from $2016$, who proposed a similar approach for OSA.
All the similar works that we are aware of also used USRP boards, and implemented the demonstration using either the Simulink and MATLAB softwares, or the GNU Radio software like we did \cite{Besson2018ICT}.
%
Indeed, the demonstrations and the works presented below are coming from our team experiments, and have been extended by the team of Sumit Darak at IIIT Delhi after his postdoctoral fellowship in our team.

In \cite{darak2016bayesian,Darak16}, the authors study the same model and focused on the \RhoRand{} policy, which was the state-of-the-art back in $2016$, combined with \UCB{} or \klUCB, as well as an extension using Bayes-UCB from \cite{Kaufmann12BUCB}.
Their idea is to use the same skeleton as \RhoRand, that is to assign a \emph{rank} to each player, and make players change their rank after any collision. But instead of selecting a new rank uniformly at random among $[M]$, they proposed to use a ``second-stage'' learning policy\footnote{This is a very natural idea: use a bandit algorithm to balance the exploration/exploitation aspect of rank selection, instead of a random hoping.}, based on Bayes-UCB, to (try to) learn the best rank while still exploring each rank from time to time.
This algorithm is implemented in SMPyBandits and named \rhoLearn,
% \footnote{See \href{https://smpybandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}{\texttt{SMPyBandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}} for its documentation.},
where it can use Bayes-UCB or any of the $65$ or more bandit algorithms available in the library.
Even if no theoretical guarantee backs up this idea of second-stage learning with Bayes-UCB, empirical simulations found that it can be efficient.
We illustrate this in Table~\ref{table:5:comparisonRhoRandRhoLearn} below, where we consider the same problem as described above in Section~\ref{sub:5:withoutSensing} (Table~\ref{table:5:meanRegretSimulationsNoSensing}).
We include different \rhoLearn{} algorithms, that uses \klUCB{}, Bayes-UCB or Exp3 for the second-stage learning,
and we include both the centralized multiple-play version of \klUCB{} and \MCTopM-\klUCB{} for comparison.

>>>>

% ----------------------------------------------------------------------------
% \subsection{Inspirations from Cognitive Radio Proof-of-Concepts}
\subsection{An idea from a Cognitive Radio Proof-of-Concept: also use learning for the rank of \RhoRand}
\label{sub:5:USRPdemos}

Similarly to our demonstration of MAB learning in an IoT network that we presented in the previous Chapter~\ref{chapter:4} in Section~\ref{sec:4:gnuradio},
we list here some related works, dating back from $2016$, who proposed a similar approach for OSA.
All the similar works that we are aware of also used USRP boards, and implemented the demonstration using either the Simulink and MATLAB softwares, or the GNU Radio software like we did \cite{Besson2018ICT}.
%
Indeed, the demonstrations and the works presented below are coming from our team experiments, and have been extended by the team of S. Darak at IIIT Delhi after his postdoctoral fellowship in our SCEE team.
%
In \cite{darak2016bayesian,Darak16}, the authors study the same model and focused on the \RhoRand{} policy, which was the state-of-the-art back in $2016$, combined with \UCB{} or \klUCB, as well as an extension using Bayes-UCB from \cite{Kaufmann12BUCB}.

Their idea is to use the same skeleton as \RhoRand{} \cite{darak2016bayesian}, that is to assign a \emph{rank} to each player, and make players change their rank after any collision. But instead of selecting a new rank uniformly at random among $[M]$, they proposed to use a ``second-stage'' learning policy, based on Bayes-UCB, to (try to) learn the best rank while still exploring each rank from time to time.
This is a very natural idea: use a bandit algorithm to balance the exploration/exploitation aspect of rank selection, instead of a random hoping.
This algorithm is named \rhoLearn, and it is implemented in SMPyBandits,
% \footnote{See \href{https://smpybandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}{\texttt{SMPyBandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}} for its documentation.},
where it can use Bayes-UCB, or any of the $65$ or more bandit algorithms available in the library.
%
Even if no theoretical guarantee backs up this idea of second-stage learning with Bayes-UCB, empirical simulations found that it can be efficient.
We illustrate this in Table~\ref{table:5:comparisonRhoRandRhoLearn} below, where we consider the same problem as described above in Section~\ref{sub:5:withoutSensing} (Table~\ref{table:5:meanRegretSimulationsNoSensing}).
We include different \rhoLearn{} algorithms, that uses \klUCB{}, Bayes-UCB or Exp3 for the second-stage learning,
and we include both the centralized multiple-play version of \klUCB{} and \MCTopM-\klUCB{} for comparison.
